Object-based Auditory Scenes Similarity Retrieval and Classification With Wavelet Scattering

### 2016-07-12 paper/structureScene.tex
replace cite to ref

\subsubsection*{MFCCs \vs scattering}
as shown in Figure \ref{folds}, scattering coefficients outperform MFCCs over all but one fold of the DCASE 2013 private dataset when applying early integration, and over all folds when applying late integration.
Not only the average accuracy is improved, but the variance between fold-wise accuracies is also reduced, \eg from $16\%$ to $7\%$ in the case of early integration.
This is in accordance with the previous results on similarity retrieval, as well as with other papers comparing mel-frequency coefficients with scattering coefficients on a variety of tasks, ranging from musical genre recognition \cite{Anden2014} to environmental sound classification \cite{Salamon2015}.

>>>>

\subsubsection*{MFCCs \vs scattering}

As shown in Figure \ref{fig:folds}, scattering coefficients outperform MFCCs over all but one fold of the DCASE 2013 private dataset when applying early integration, and over all folds when applying late integration.
Not only the average accuracy is improved, but the variance between fold-wise accuracies is also reduced, \eg from $16\%$ to $7\%$ in the case of early integration.
This is in accordance with the previous results on similarity retrieval, as well as with other papers comparing mel-frequency coefficients with scattering coefficients on a variety of tasks, ranging from musical genre recognition \cite{Anden2014} to environmental sound classification \cite{Salamon2015}.
